Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-09-25 manuscript/paper-tycho.tex
More paper; full model simulations

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
remnants may exhibit thin ($\abt1$--$10$\% of shock radius) X-ray rims of synchrotron
radiation from forward shock-accelerated electrons that travel downstream of
the shock and quickly cease to radiate. Rim widths limited by radiative energy
losses should decrease with energy and require magnetic field amplification
$10$--$100\times$ that expected from adiabatic shock compression.  Damped
magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
on SN 1006. Inferred magnetic fields, diffusion coefficients, and
diffusion-energy scaling may constrain models for cosmic ray acceleration in
supernova remnants and plasma turbulence in astrophysical shocks.
\end{abstract}

@@

% ============
% Introduction
% ============
\section{Introduction}

\note[Aaron]{this first draft of intro structure is mostly set (in terms of
material, number of paragraphs).  Explanations/etc may be too simplistic, I
have more reading to do.}

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated ISM/CSM particles in young supernova remnants emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
morphology with bright X-ray and radio rims/filaments due to line-of-sight
projection (hereafter, thin rims).
Seminal observations \& interpretations of these filaments, interpretation in
context of DSA.  Attempts to model filaments and figure out what's going on.
Why do we care about these models?  They tell us something about what happens
behind the shock, and perhaps what's going on at the shock.  We get at the
plasma and magnetic field turbulence, electron injection.
Applications to: cosmic ray acceleration, turbulent field amplification, (note
assumptions in re proton/electron spectra).
Cut-off energy of injected electrons?
Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and diffusion (\emph{driven by
collisionless particle interaction, magnetic field turbulence, ?????  fill in
details}) with respect to bulk advection.  Energy-dependent diffusion (e.g.,
diffusion coefficient $D \propto E$ for Bohm diffusion) allows higher energy
electrons to diffuse further upstream or downstream than would be expected from
pure advection; in particular, diffusion upstream of the shock may give rise to
a shock precursor \citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.
Finally, the magnetic field strength may be quickly damped behind the shock, so
that electrons may not radiate as efficiently and thin rims would reflect the
spatial structure of the field, rather than efficient particle acceleration
(and losses) and/or efficient synchrotron cooling \citep{pohl2005}.

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Synchrotron loss-limited rims should scale as $w
\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
effect at higher energies, yielding a slower drop-off in rim widths when
diffusion dominates.  Magnetic damping, if at a length scale comparable to
filament widths, predicts energy-independent rim widths -- intuitively, if the
magnetic field turns off, synchrotron radiation turns off regardless of
electron energy.  \citet{ressler2014} give a much fuller exposition of the
relative effects of advection, diffusion, and magnetic field damping.

% Which one is right?
Which mechanisms are most relevant to historical SNRs?
\note[Aaron]{need to read more / more thoroughly}
Introduce $\tsynch$ and the basic intuition. Explain why diffusion is important
(when did diffusion start being recognized as relevant to SNR filaments? or how was
this shown?).
Following Sean (i.e., taking all of his references), relevant previous
observational studies.
\citet{bamba2003, vink2003, yamazaki2004, ballet2006} consider advection and
diffusion separately (with the break-point at $\Ecut$ when advective and
diffusive length scales are equal;
\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
with the catastrophic dump equation.
\citet{berezhko2003, berezhko2004, cassam-chenai2007, morlino2010, rettig2012}
consider diffusion and advection simultaneously with the continuous loss
equation instead.
Conclusion that magnetic fields are amplified according to loss-limited model.  How?  Field
amplification from plasma instabilities, evidence for stronger compression ratios?
\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
understand.
\citet{rettig2012} mention independent estimates of magnetic field, from
\citet{acero2010, acciari2011} for SN 1006 and Tycho (considering gamma-ray,
radio, X-ray data).

Magnetic damping offers a tantalizing alternate explanation and has not
been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
\citet{rettig2012} gave model predictions for several historical SNRs and
proposed discriminating based on filament spectra -- the
expectation is that damped spectra are softer, loss-limited harder.
\citet{ressler2014} developed the idea of investigating energy dependence and
found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
model.

% Why Tycho's SNR
To further test these models, we turn to the remnant of Tycho's 1572 supernova
(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
its rims are well-resolved by \textit{Chandra}'s spatial resolution.  Tycho has
an extensive and unusually contiguous shell of synchrotron rims around its
periphery, consistent with expansion into a low density ISM; ISM.
\citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
\unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
\citep{williams2013} and interacting with a molecular cloud on its eastern limb
\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
more consistent shock acceleration around its periphery than in other
historical remnants, whether of Type Ia or CC SNe \note[Aaron]{this is not really
justifiable, but I think it's worth noting something to this effect?}.
CR acceleration evidence in Tycho, if relevant? \citet{eriksen2011,
acciari2011}.

% Paper roadmap
\note[Aaron]{roadmap}
We measure Tycho's rim widths, following the work of \citet{ressler2014}
(hereafter, \citetalias{ressler2014}) on the remnant of SN 1006.
We make measurements to distinguish between two main scenarios
(explain how diffusion/advection competition come into this).
Our procedure, in both measurement and rim width modeling, follows that of
\citetalias{ressler2014} with only slight modifications.
We first select regions around Tycho's forward shock for analysis, measure
rim widths, and verify that rim spectra are free of thermal line emission.
Using two models for particle transport, we fit measured widths...
We discuss the implications of our fits and models for magnetic shock
amplification (lending credence to previous estimates, in disfavoring magnetic
field amplification), and discuss particle diffusion/acceleration at the shock.
Any further misc. applications (constraints on precursors, etc).

% TODO Chunk of text I don't know what to do with...
We briefly review relevant particle transport models that we use to fit our
measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
In particular, the transport models
account for both advection and diffusion simultaneously, as opposed to
considering the lengthscales separately with advection dominating below a
critical energy and diffusion, above
\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
\note[Aaron]{clarify, be more specific}.
The effects of varying various parameters, especially in regards to filament
energy dependence, are explored in detail by \citetalias{ressler2014}.

@@

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
transport from initial injection at the remnant's forward shock as following
the advection-diffusion equation given by:
\note[Aaron]{ApJ prefers bold vectors and vector operators, fix later}
% TODO fix vector operators
\begin{equation}
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\end{equation}
where $f = f(E,x)$ is electron distribution as a function of electron energy
$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
By considering 1-D steady-state plane transport at a constant downstream
velocity $v_d$ \note[Aaron]{we threw out 1. spherical coordinate terms, and 2.
compressible flow terms, I think.  Is the latter justifiable?  Makes sense for
assumption of uniform downstream velocity -- but is this a safe assumption in
practice?  Double check order-of-magnitude...} and a space-independent diffusion
coefficient, we obtain:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
The source/sink term $C$ is determined by our assumptions about the injected
electron energy spectrum and its time/space evolution.

A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
which is equation (5) of \citetalias{ressler2014}.
\note[Aaron]{I think there should be a delta function for e- injection, but it
probably doesn't affect the solution.  Double check.}
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
take $\beta = 4.6$ assuming projection from spherical shell, as derived by
\citet{ballet2006}.

A more advanced model is given by accounting for continuous radiation energy
losses while electrons are transported downstream:
\begin{equation} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/\Ecut} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citetalias{ressler2014}.  The injected electron
distribution is an exponentially cut-off power law with normalization $K_0$ and
cut-off energy $\Ecut$; the cut-off energy is determined by the form of the
diffusion coefficient $D$, which we discuss in
Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
numerically solve for electron distribution $f(E,x)$ using Green's function
solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
given using notation close to that of this paper by \citetalias{ressler2014}.
The electron distribution may then be integrated to obtain synchrotron
emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical shell yields intensity:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  We can then compute these
integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
model predictions for rim FWHMs.

@@

\subsection{Diffusion energy-dependence} \label{sec:diffcoeff}

The modus operandi of previous work has been to assume Bohm diffusion, or at
least Bohm diffusion-energy scaling.  Bohm diffusion makes the
assumption that particle mean free path, and hence the diffusion coefficient,
is proportional to the particle gyroradius, yielding $D \propto E$.

\citet{reynolds2004} suggested that physically motivated models of MHD
turbulence could give rise to non-linear diffusion-energy scalings, assuming
quasi-linear turbulence \note[Aaron]{read more}.
Specifically, power-law energy-wavenumber spectra for Kolmogorov and Kraichnan
turbulence predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.

We consider a generalized diffusion coefficient that allows arbitrary
power-law dependence of diffusion upon energy:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
\end{equation}
As the diffusion coefficient is energy dependent, we rewrite the diffusion
coefficient in terms of a fiducial energy $E_h = 2 \unit{keV}$ throughout, with
$\eta_2 = \eta_h$.  The constant $\eta_2$ is the diffusion coefficient at
$2 \unit{keV}$ scaled by the Bohm diffusion value.
\note[Aaron]{Also give some intuition of relation of $D$ and $\Ecut$ to relate to
previous studies.}

Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
Explain the basic interplay between diffusion and magnetic field, in
controlling rim widths.

With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and acceleration timescales;
the acceleration timescale is determined from the theory of diffusive shock
acceleration.  The cut-off energy, following \citet{parizot2006}, is given as:
\begin{align*}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
        \left[
            \frac{E_h^{\mu - 1}}{\eta}
        \right]^{1 / (1 + \mu)}
\end{align*}
\note[Aaron]{This differs from Sean's presentation -- I drew this from the
Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
$E_h$ ?!  Come back to this shortly.}

>>>>

\begin{abstract}
Many young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims are strong evidence for strong
magnetic field amplification, requiring shock-accelerated electrons to radiate
and cool rapidly downstream of the shock.  But, magnetic field damping
immediately behind the shock could produce similarly thin rims.  Synchrotron
loss-limited rim widths should decrease with energy whereas damping limited
rims should be relatively energy-independent.  To discriminate between models,
we measured rim widths around Tycho's supernova remnant in 5 energy bands using
an archival $750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing
energy, favoring loss-limited radiation over magnetic damping and corroborating
similar observations in the remnant of SN 1006 (Ressler et al., 2014).
Observed widths are best fit by electron transport models requiring amplified
magnetic fields of $\abt200$--$1000 \unit{\mu G}$ and particle diffusion
coefficients $\abt 1$--$100\times$ Bohm values, consistent with prior work
on Tycho's SNR.  Non-negligible diffusion results in some degeneracy between
magnetic field strength and diffusion coefficient in setting observed rim
widths, but strong magnetic fields are required for all measurements.  A
different approach may be needed to better constrain diffusion at supernova
remnant shocks.
\end{abstract}

@@

% ============
% Introduction
% ============
\section{Introduction} \label{sec:intro}

% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
synchrotron emission due to accelerated electrons does not imply acceleration
of an unseen hadronic component, the prevailing theory of diffusive shock
acceleration (DSA) should operate on both protons and electrons.  Observations
of these synchrotron rims, with other lines of direct and indirect evidence,
have built a case for hadron and lepton acceleration up to $\unit{PeV}$
energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
acero2010, ackermann2013} \note[Aaron]{up to PeV energies for both populations?
Do protons reach higher energies with lower synchrotron losses?}. Efficient
hadron acceleration, if able to convert $\abt10\%$ of a supernova's $10^{51}
\unit{erg}$, is a prime candidate source for galactic cosmic rays up to the CR
spectrum ``knee'' \citep{vink2012}.

Spectral and spatial measurements of synchrotron rims can help constrain
physical parameters of the shock acceleration process.  Many previous workers
have inferred strong magnetic field amplification at SNR shocks, as electrons
must radiate energy rapidly to account for the thinness of observed rims.
\note[Aaron]{flesh out} Plasma physics details -- Bell's cosmic ray current
instability \citep{bell2001} ties magnetic field amplification w/ maximum CR
energy (push towards and just above the PeV limit).  How to get large
compression ratios (why is 10 an upper bound suggested by Parizot), magnetic
fields -- how far can amplification go?
The processes observed in SNR shocks are broadly relevant to many collisionless
astrophysical shocks, such as Earth's bow shock, stellar wind-blown bubbles,
starburst galaxies \citep{heckman1990}, jets of active galactic nuclei, galaxy
clusters \citep{van-weeren2010}, and even cosmological shocks
\citep{miniati2000, ryu2008}.  Reviews of diffusive shock acceleration have
ably highlighted the ubiquity of shock acceleration in astrophysical settings
\note[Aaron]{too trite?} \citep[e.g.,][]{blandford1987, malkov2001}.

% What makes these shocks?
The widths of these X-ray rims are thought to be controlled by a combination of
synchrotron losses, particle transport, and magnetic fields immediately
downstream of the shock.  Synchrotron losses depend on the initial electron
energy distribution and the gradual decrease of electron energies downstream of
the shock.  High energy electrons near the shock efficiently radiate harder
synchrotron X-ray photons, but decline in energy as they are transported away
from the shock; this may be seen in spectral softening downstream of the shock
\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
plasma advection downstream of the shock and particle diffusion with respect to
bulk advection.  In general, diffusion allows higher energy electrons to
diffuse further upstream or downstream than would be expected from pure
advection.  Finally, the magnetic field strength may be quickly damped behind
the shock, so that electrons may not radiate as efficiently and thin rims would
reflect the spatial structure of the field, rather than efficient particle
acceleration (and losses) and/or efficient synchrotron cooling
\citep{pohl2005}.

% Energy dependence.
Moreover, these controlling mechanisms predict different scalings for rim width
as a function of energy.  Synchrotron loss-limited rims should scale as $w
\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
effect at higher energies, yielding a slower drop-off in rim widths when
diffusion dominates.  Magnetic damping, if at a length scale comparable to
filament widths, predicts comparatively energy-independent rim widths --
intuitively, if the magnetic field turns off, synchrotron radiation turns off
regardless of electron energy.  \note[Aaron]{this would benefit from
numbers/quantification, I think this statement is stronger if the magnetic
field is stronger -- compare Figure 1 of \citet{pohl2005}} \citet{ressler2014}
give a much fuller exposition of the relative effects of advection, diffusion,
and magnetic field damping on filament rim widths.

% Which one is right?
Previous work has used the typical scale width of the filaments to derive
magnetic field estimates, among other physical parameters.  Observed
synchrotron spectrum roll-offs at X-ray energies require corresponding cut-offs
in the electron spectrum \citep{reynolds1998}; such a cut-off is naturally
predicted by DSA balanced against synchrotron losses, and requires that
diffusion and advection are both important near the electron cut-off energy
\note[Aaron]{imprecise statement...} Whether accounting for advection and
diffusion independently, or jointly in more sophisticated transport models, It
became clear that magnetic field amplification was necessary to explain the
observed filaments \citet{bamba2003, vink2003, parizot2006}.  \note[Aaron]{this
is said 3 paragraphs above already}

% Magnetic damping...
Magnetic damping immediately behind the shock offers a tantalizing alternative
explanation for filament rims that requires less extreme magnetic field
amplification, and damping has not been fully tested \citep{pohl2005,
marcowith2010}.  \citet{cassam-chenai2007} examined radio and X-ray synchrotron
rim profiles, but found that neither damping nor synchrotron losses matched
radio profiles particularly well.  \citet{araya2010} measured rims at multiple
energy bands in Cas A, but suggested that the rims only narrow more weakly than
expected and did not consider magnetic damping.  \citet{rettig2012} gave model
predictions for several historical SNRs and proposed discriminating based on
filament spectra -- the expectation is that damped spectra are softer,
loss-limited harder.  \citet{ressler2014}, using deep observations of SN 1006
from a recent \Chandra Large Project, fully developed the idea of
differentiating damping and loss-limited scenarios by using rim width energy
dependence and found rim narrowing in the remnant of SN 1006, strongly favoring
a loss-limited model.

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} by measuring rim
widths at multiple energies in the remnant of Tycho's 1572 supernova
(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
its rims are well-resolved by \textit{Chandra}'s spatial resolution; the work
is further made possible by a deep $750 \unit{ks}$ exposure of the entire
remnant, yielding excellent count rates and allowing us to sample the rims
quite finely.  Tycho has an extensive and unusually contiguous shell of
synchrotron rims around its periphery, consistent with expansion into a low
density ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt
0.1$--$0.2 \unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
\citep{williams2013} and interacting with a molecular cloud on its eastern limb
\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
more consistent shock acceleration around its periphery than in other
historical remnants, whether of Type Ia or CC SNe.

Evidence for acceleration: spectral softening \citep{cassam-chenai2007}, CD-FS
gap \citep{warren2005}, multi-wavelength observations \citep{acero2010,
acciari2011, morlino2012} for SN 1006 and Tycho; Tycho's tiger stripes
\citep{eriksen2011}. These further support the notion that Tycho is actively
accelerating hadrons and leptons.
Various questions to consider (or answer).
Why the diversity of filament structure? How does diffusion really work?  How
much energy is going into cosmic rays / how efficient is the acceleration
process?  All sorts of things... (one interesting paper: \citet{caprioli2013}).
\note[Aaron]{this para may not be necessary}

% Paper roadmap
Our measurements and modeling closely followed and extended the procedure of
\citet{ressler2014} (hereafter, \citetalias{ressler2014}).  We first briefly
review relevant transport models which fully account for electron advection and
diffusion with continuous synchrotron losses, as considered by, e.g.,
\citet[and references therein]{berezhko2004} and \citet{rettig2012}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using
our model for particle transport (with DSA included, to first order, in a
simple exponentially cut-off injected electron spectrum), we obtain estimates
on magnetic field strength and diffusion coefficient as a function. \emph{We
discuss the implications of our model fit results for particle transport in
Tycho, despite a significant degeneracy between diffusion and synchrotron
losses when diffusion is non-negligible.}
\note[Aaron]{(tentative?)}
\note[Aaron]{(non sub-Bohm, or anything above Bohm basically)}

@@

% TODO Chunk of text I don't know what to do with...
We consider two models for particle transport to our measurements of Tycho's
filament widths.  To best quantify width-energy dependence, we measure rim full
widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
measurements to these models' predictions of rim FWHMs at multiple photon
energies.  \citetalias{ressler2014} give a fuller review of previous approaches
to characterizing filament widths, as well as a more thorough exposition of
model parameters and physical implications.

%Early workers measured filament widths of several historical supernova remnants
%and considered ...  Assuming that thin rim widths are limited by synchrotron
%energy losses (loss-limited rims), you have $l_{\mt{ad}} \propto v_d \tsynch$
%gives a magnetic field...  \citet{bamba2003, vink2003, yamazaki2004,
%ballet2006} More sophisticated models have followed, but the basic result is
%consistent -- magnetic fields are amplified, with some amount of diffusion.
%\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
%with the catastrophic dump equation.  \citet{berezhko2003, berezhko2004,
%cassam-chenai2007, morlino2010, rettig2012} consider diffusion and advection
%simultaneously with the continuous loss equation instead.  DSA may be
%incorporated by direct calculation, or by assumption of a resultant electron
%spectrum and cut-off \citep[e.g.,][]{zirakashvili2007}.
%\citet{morlino2010}, and references therein, consider particle transport in the
%context of nonlinear DSA neglecting particle energy losses (as would be
%relevant for accelerated protons).  All the same principles.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose much material is not relevant or
condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $E/3 (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
transport from initial injection at the remnant's forward shock as following
an advection-diffusion equation given by:
\begin{equation}
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\end{equation}
where $f = f(E,x)$ is electron distribution as a function of electron energy
$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
By considering 1-D steady-state plane transport at a constant downstream
velocity $v_d$ and a space-independent diffusion coefficient, we obtain:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
For simplicity, the source/sink term $C$ and diffusion coefficient $D$
encapsulate all assumptions about the DSA-generated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  We also consider only particle transport downstream of the
shock ($x \geq 0$).  More sophisticated treatments may explicitly treat
magnetic fields across the shock, plasma streaming instabilities and particle
losses, anisotropic diffusion, the DSA process and efficiency, and other
details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary
\note[Aaron]{I don't have a citation, but it seems simple enough?}.
\citet{parizot2006} employed this model to derive estimates of magnetic fields,
diffusion coefficients, and electron spectrum cut-offs for several historical
SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
FWHM predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{berezhko2004, cassam-chenai2007, morlino2010, rettig2012}; and
references therein.  The cut-off energy is determined by the form of the
diffusion coefficient $D$, which we discuss in Section~\ref{sec:diffcoeff}.
(but, cf. \citet{zirakashvili2007} on the exponential cut-off assumption) To
determine rim profiles and widths, we first numerically solve for electron
distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
and \citet{rettig2012}; these solutions are given by \citetalias{ressler2014}
using notation similar to that used herein \note[Aaron]{wording}.  The electron
distribution may then be integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

@@

% Diffusion
\subsection{Diffusion energy-dependence} \label{sec:diffcoeff}

\note[Aaron]{can condense this, merge first 2 paragraphs here?}
The modus operandi of much previous work has been to assume Bohm diffusion or
diffusion-energy scaling ($D \propto E$).  Bohm diffusion assumes that the
particle mean free path $\lambda$ is equal to the gyroradius $r_g = E/(eB)$,
yielding diffusion coefficient $D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$.
We may generalize by adding a prefactor $\eta$ such that $\lambda = \eta r_g$:
\begin{equation} \label{eq:bohm}
    D = \frac{\lambda c}{3} = \frac{\eta c E}{3 e B} .
\end{equation}
Here, and throughout, we use CGS (Gaussian) units; $c$ is the speed of light,
$E$ is particle energy, $e$ is elementary charge, and $B$ is magnetic field.
Bohm diffusion at $\eta = 1$ is commonly considered a lower
limit on the diffusion coefficient at all energies, but sub-Bohm diffusion may be
possible in turbulently amplified oblique magnetic fields
\citep[e.g.,][]{reville2013}, and has not been well-studied.
\note[Aaron]{I have no justification, and minimal sense, of whether this is
correct or not.  Any treatment/discussion of Bohm diffusion?  All the papers
seem to take it for granted} Different types of MHD turbulence, in a
quasi-linear approximation for particle motion, may give rise to a non-linear
energy scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence predict $D
\propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.  For gyroradius larger
than field coherence length, $\mu = 2$ may be relevant as well.
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing}

In our models, we consider a generalized diffusion coefficient that with
arbitrary power-law dependence of diffusion upon energy:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu .
\end{equation}
This follows, e.g., \citet{parizot2006}; note that $\eta$ now has units of
$\mathrm{erg}^{1-\mu}$.  In the right-hand side of
equation~\eqref{eq:diffcoeff} we also rescale the diffusion coefficient to its
value at a fiducial energy $E_h$, ; the now dimensionless $\eta_h$ is the
diffusion coefficient scaled to the Bohm value at $E_h$.  We choose fiducial
electron energy $E_h$ corresponding to a synchrotron photon energy of $2
\unit{keV}$, taking the $\delta$-function approximation that an electron of
energy $E$ radiates solely at frequency $\nu \propto E^2 B$ in a surrounding
magnetic field.  Then $E_h \propto \sqrt{2 \unit{keV} / B}$.  The value of
$E_h$ does depend on the user/model value of magnetic field $B$, but having
$\eta_h$ tied to observations at $2 \unit{keV}$ gives a convenient and
intuitive sense of diffusion strength when applied to any remnant.
